%-----------------------------------------------------------------------------------------------------
% AUTHOR: Soumitra Samanta (soumitra.samanta@gm.rkmvu.ac.in)
%-----------------------------------------------------------------------------------------------------

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
								\usepackage{graphics}                 % Packages to allow inclusion of graphics
\usepackage{hyperref}                 % For creating hyperlinks in cross references
\usepackage{url}
\usepackage{concmath,mathtools,url}
\usepackage{natbib}

\usepackage{amssymb}
\usepackage{color}
\usepackage{enumitem}% http://ctan.org/pkg/enumitem

%SetFonts

%SetFonts

\title{Project title}
\author{Group name\\
Project member's names (all)\\
Email address of all members}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

\section*{Abstract}

Project summary in 8-10 sentences (max 100 words).

\section{Introduction}
A brief description of your project (you should explain about your project to answer what?, why? and how?).

\section{Literature review}
Literature survey related to your project (What others have done related to your project and what is the main difference between your proposed method and the existing methods).

\section{Proposed methodology}
Here is your proposed method to tackle the above problem. You should describe your methods in details.

\section{Experimental result}

You should evaluate your proposed method with standard/state-of-the-art datasets. In this section you should describe the following:

\begin{itemize}
	\item Datasets you have used for your project
	\item Experimental settings 
	\item Experimental results and comparison with the state-of-the-art methods
	\item Time complexity
\end{itemize}


\section{Summary}

In this section, you have to summarise your project

\section{References}

Some references related to your project. I am attaching a \textit{nlp\_reference.bib} file and you can use that. You have to add your \textit{bibtex} according to your references {like conference, journal, book, etc.}. Your reference section should be some like bellow:


\nocite{*}% Biblography without citation!
	
\bibliography{ml_reference} % .bib file
\bibliographystyle{plain}


\end{document}  